Makefile, compiliation notes

### 2018-06-25 makefile.Rmd
trivial

---
title: "Makefile_linux, compiliation notes"
author: "Daniel Reuman"
date: ""
output: pdf_document
---

>>>>

---
title: "Makefile, compiliation notes"
author: "Daniel Reuman"
date: ""
output: pdf_document
---

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
library(captioner)
library(rmarkdown)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```
